Simultaneous comparisons of diversity indices estimated from metagenomic data
==============================================================================

The following "GlobalPatterns" data set is from the [phyloseq package](http://joey711.github.io/phyloseq/) on Bioconductor. This packages allows the import of OTU-tables from qiime, mothur and other software packages for sequence data. Once the data is imported into R, it is stored in a phyloseq object, which is a specialized system of S4-classes. 

First, we install phyloseq with dependencies from Bioconductor if not already installed.

```{r eval = FALSE, prompt=TRUE}
source("http://bioconductor.org/biocLite.R")
biocLite("phyloseq")
```

Next, we load the phyloseq packages to get the GlobalPatterns data set. For pre-processing steps of the sequence data, see the phyloseq vignettes.

```{r, message=FALSE, warning=FALSE ,prompt=TRUE}
library(phyloseq)
data(GlobalPatterns)
GP <- prune_species(speciesSums(GlobalPatterns) > 0, GlobalPatterns)
```

Phyloseq offers several functions to access variables in the object. 

```{r, prompt=TRUE}
sample_variables(GlobalPatterns)
```

```{r, prompt=TRUE, fig.width=10, fig.height=5}
plot_richness(GP, x = "SampleType", color = "SampleType", shsi = TRUE)
```

Will be continued soon...


